---
title: "DataGeneration"
author: "Avery Chan"
date: "11/21/2021"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Why is this shit so broken?
library(tidyverse)
```

```{r}
data <- read_tsv("world-country-names.tsv")

data <- data %>% mutate(
  new_info = abs(id) + utf8ToInt(name)
)

# write_tsv(data, "my_data.tsv")
# read_tsv("my_data.tsv")
```

```{r}
ind <- read.csv("data/Indicators.csv")
```

```{r}
ind <- ind %>% 
  mutate(
    IndicatorName = str_replace_all(IndicatorName, " ", "_")
  )
ind_names <- ind$CountryName %>% unique()
data_names <- data$name

ind_names %>% length()
data_names %>% length()

overlap_names <- intersect(ind_names, data_names)

overlap_names %>% length()
ind <- ind %>% filter(CountryName %in% overlap_names)
```

```{r}
ind %>% group_by(IndicatorName) %>% 
  summarise(
    n = n()
  ) %>% arrange(-n)

# ind %>% group_by(IndicatorName, CountryName) %>% 
#   summarise(
#     val = mean(Value)
#   )

country_count <- ind %>% group_by(IndicatorName, CountryName) %>%
  summarise(
    n = n()
  ) %>% 
  ungroup() %>% 
  group_by(IndicatorName) %>% 
  summarise(
    n = n()
  )
country_count %>% arrange(-n)
country_count$n %>% hist()

ind_more_140 <- country_count %>% filter(n > 170) %>% select(IndicatorName)
```


```{r}
# ind %>% group_by(CountryName) %>% 
#   summarise(
#     
#   )

# ind$IndicatorName
# ind$Value
ind$IndicatorName %>% unique()

ind2 <- ind %>% filter(IndicatorName %in% ind_more_140$IndicatorName)
```

```{r}
# ind2 %>% group_by(IndicatorName) %>% 
#   summarise(
#     n = n()
#   ) %>% arrange(-n)
country_count %>% filter(n > 170) %>% arrange(-n)
```


```{r}
grouped <- ind2 %>% 
  select(CountryName, IndicatorName, Value) %>% 
  pivot_wider(
  names_from = IndicatorName,
  values_from = Value,
  values_fill = NA
)

# grouped %>% mutate_all(
#   map_chr(., toString)
# )

# grouped %>% mutate_if(
#   
# )

listToChar <- function(x) map_chr(x, toString)

ind_grp <- grouped %>% mutate_at(
  vars(-CountryName),
  listToChar
)
write_tsv(ind_grp, "grouped.tsv")

# grouped %>% mutate(
#   `Adolescent fertility rate (births per 1,000 women ages 15-19)` = map_chr(`Adolescent fertility rate (births per 1,000 women ages 15-19)`, toString)
# )
# grouped %>% mutate(
# )
# write_tsv(grouped, "grouped.tsv")

ind_grp <- ind_grp %>% rename(
  name = CountryName
)
final_data <- data %>% full_join(ind_grp)
write_tsv(final_data, "my_data.tsv")
```

# chosen indicators

## Simple

### Population
Population_growth_(annual_%)
Population,_total
Population_density_(people_per_sq._km_of_land_area)
Rural_population	
Rural_population_(%_of_total_population)	
Urban_population	
Urban_population_(%_of_total)
Mortality_rate,_adult,_male_(per_1,000_male_adults)	
Mortality_rate,_adult,_female_(per_1,000_female_adults)	

### Land
Surface_area_(sq._km)
Land_area_(sq._km)

## Complex

Access_to_electricity_(%_of_population)	
Arable_land_(%_of_land_area)	
Intentional_homicides_(per_100,000_people)
Share_of_women_in_wage_employment_in_the_nonagricultural_sector_(%_of_total_nonagricultural_employment)
Mobile_cellular_subscriptions
Labor_force_participation_rate,_total_(%_of_total_population_ages_15+)_(national_estimate)	
Ratio_of_female_to_male_labor_force_participation_rate_(%)_(national_estimate)	
CO2_emissions_(metric_tons_per_capita)	

### Economics
GDP_per_capita_(current_US$)	
GDP_growth_(annual_%)
GDP_per_capita_growth_(annual_%)
General_government_final_consumption_expenditure_(%_of_GDP)	
Household_final_consumption_expenditure,_etc._(%_of_GDP)	

### Education
Theoretical_duration_of_primary_education_(years)	
Enrolment_in_primary_education,_both_sexes_(number)	
Enrolment_in_secondary_general,_both_sexes_(number)
Percentage_of_students_in_primary_education_who_are_female_(%)
Percentage_of_students_in_secondary_general_education_who_are_female_(%)














